---
output: md_document
---
# Hierarchical Integrative Grouped LASSO
Environmental health studies are increasingly measuring multiple pollutants
to characterize the joint health effects attributable to exposure mixtures.
However, the underlying dose-response relation- ship between toxicants and
health outcomes of interest may be highly nonlinear, with possible nonlinear
interaction effects. Hierarchical integrative group LASSO (HiGLASSO) is a
general shrinkage and selection framework to identify noteworthy nonlinear
main and interaction. HiGLASSO is broadly applicable for studying potential
nonlinear main and interaction effects in the presence of group structures
among a set of exposures.

## Installation
`higlasso` can be installed via Github using `devtools`

```{r, eval = F}
# install.packages("devtools")
devtools::install_github("umich-cphds/higlasso")
```
You'll need a working C++11 compiler, which can obtained by installing Xcode on
MacOS, and RTools on Windows.
## Example

`higlasso` can be slow, so it may may be beneficial to tweak some its settings
(for example, `nlambda1` and `nlambda2`) to get a handle on how long the method
will take before running the full model.

```{r, eval = F}
library(higlasso)

X <- as.matrix(higlasso.df[, paste0("V", 1:10)])
Y <- higlasso.df$Y
Z <- matrix(1, nrow(X))

# This can take a bit of time
cv.fit <- cv.higlasso(Y, X, Z)

```

## Bugs
If you encounter a bug, please open an issue on the
[Issues](https://github.com/umich-cphds/higlasso/issues) tab on Github or send
us an email.

## Contact
For questions or feedback, please email Jonathan Boss at
<bossjona@umich.edu> or Alexander Rix <alexrix@umich.edu>.

## References
