---
output: md_document
---

<!-- Badges -->
[![CRAN Version](https://img.shields.io/cran/v/mianet?style=flat-square&color=blue&label=CRAN)](https://cran.r-project.org/package=higlasso)
[![GitHub Release](https://img.shields.io/github/v/release/umich-cphds/higlasso?include_prereleases&label=Github&style=flat-square&color=blue)](https://github.com/umich-cphds/higlasso)
[![Travis CI](https://img.shields.io/travis/umich-cphds/higlasso?style=flat-square)](https://travis-ci.org/umich-cphds/higlasso)

# Hierarchical Integrative Group LASSO
Environmental health studies are increasingly measuring multiple pollutants to
characterize the joint health effects attributable to exposure mixtures. However,
the underlying dose-response relationship between toxicants and health outcomes
of interest may be highly nonlinear, with possible nonlinear interaction effects.
Hierarchical integrative group LASSO (HiGLASSO) is a general shrinkage and
selection framework to identify noteworthy nonlinear main and interaction
effects in the presence of group structures among a set of exposures.

## Installation
`higlasso` can be installed via Github using `devtools`

```{r, eval = F}
# install.packages("devtools")
devtools::install_github("umich-cphds/higlasso")
```
You'll need a working C++11 compiler, which can obtained by installing Xcode on
MacOS, and RTools on Windows.

## Example
`higlasso` can be slow, so it may may be beneficial to tweak some its settings
(for example, `nlambda1` and `nlambda2`) to get a handle on how long the method
will take before running the full model.

```{r, eval = T}
library(higlasso)

set.seed(48109)

X <- as.matrix(higlasso.df[, paste0("V", 1:10)])
Y <- higlasso.df$Y
Z <- matrix(1, nrow(X))

# This can take a bit of time
fit <- cv.higlasso(Y, X, Z)

print(fit)
```

## Bugs
If you encounter a bug, please open an issue on the
[Issues](https://github.com/umich-cphds/higlasso/issues) tab on Github or send
us an email.

## Contact
For questions or feedback, please email Jonathan Boss at
<bossjona@umich.edu> or Alexander Rix <alexrix@umich.edu>.

## References
